\cventry{2017--Present}{Faculty Senator}{Johns Hopkins Bloomberg School of Public Health}{}{}{
Helped lead a discussion on scientist-track faculty and representation in the school and represented the department of Biostatistics.
}

\cventry{2013--Present}{Middle Manager}{\href{http://www.thread.org/}{Thread/Incentive Mentoring Program}}{}{}{
Interfaced between executive-level staff and lower-level management.  Organized monthly meetings, weekly progress updates and e-mails, and provided broad-scale mentorship for high-school students in the Baltimore City school district.  Program title was "Grandparent", as it is a family-based, positive change model.
}
\cventry{2013--Present}{Co-founder, Vanguard Scholarship}{Sun Valley High School}{}{}{
Co-founded a scholarship for outstanding students attending my alma mater, Sun Valley High School.  Interviewed students as a representative of a graduate doing science at mock interview day. Continually recruiting other graduates to become involved and fund raising.
}
\cventry{2014}{Organizer, Journal Club}{JHSPH Department of Biostatistics}{}{}{}
\cventry{2013-2015}{Founder/Organizer, Writing Accountability Group}{\newline JHSPH Department of Biostatistics}{}{}{}
\cventry{2013-2014}{Founder/Organizer, Blogging Club}{\newline JHSPH Department of Biostatistics}{}{}{}
\cventry{2010--2013}{Manager}{\href{http://www.thread.org/}{\newline Thread/Incentive Mentoring Program}}{}{}{
Title was a ``Head of Household''; mentored and tutored a student from Dunbar High School, teaching coursework, life skills, support as needed.
}
