\cventry{2014--present}{Co-Instructor}{JHSPH}{Introduction to R for Public Health Researchers}{}{
Co-developed a one-week, 8-hour-a-day course in the Winter and Summer Institutes at Johns Hopkins with Dr.~Andrew Jaffe.  Developed 50\% of code and slides for presentation and recorded lectures delivering slides.
}{}

\cventry{2020}{Instructor}{ENAR}{R package development}{}{
Developed and instructed a tutorial on R package development.  Created of all code and slides for presentation; a 1-hour, 45 minute tutorial.
}{}


\cventry{2019}{Instructor}{SMI}{R Software Development Workshop}{}{
Co-developed and instructed a tutorial on R package developed for 40 statisticians.  Ran the workshop and delivered a 2 hour tutorial with Dr. Amanda Mejia.
}{}


\cventry{2018}{Instructor}{ENAR}{Neuroimaging Analysis within R}{}{
Co-developed and instructed a tutorial for 20 statisticians.  Created 75\% of all code and slides for presentation and presented for half of the 4-hour session.
}{}


\cventry{2016--2017}{Co-instructor}{JHSPH}{Advanced Data Science}{}{
Provides an intensive introduction to applied statistics and data analysis. Since both data analysis and methods development require substantial hands-on experience, focuses on hands-on data analysis. 
}{}

\cventry{2017}{Instructor}{ISBI}{Neuroimaging Analysis within R}{}{
Co-developed and instructed a tutorial for 30 biomedical engineers.  Created 75\% of all code and slides for presentation and presented for half of the 4-hour session.
}{}

\cventry{2015}{Instructor}{ENAR}{A Tutorial for Multisequence Clinical Structural Brain MRI}{}{
Co-developed and instructed a tutorial for 35 statisticians.  Created 75\% of all code and slides for presentation and presented for half of the 3-hour session.
}{}

\vspace{1em}
\cventry{2015}{Instructor}{Coursera}{Neurohacking with R}{}{
Co-developed a MOOC (massive open online course) for \href{https://www.coursera.org/}{Coursera} on neuroimage processing and statistical analysis completely within R.  Developed 50\% of code and slides for presentation and recorded lectures delivering slides.
}{}


