%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% UMass Graduate Application Personal Statement
% Authors
%  Erik Erhardt
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Build this latex document with the following commands:
% latex filename.tex
% latex filename.tex
%     creates dvi file from tex file
% dvips filename.dvi
%     creases ps file from dvi file

% TO VIEW
% xdvi filename.dvi
%     to view dvi file
% ghostview filename.ps
%     to view ps file

% TO PRINT
% dvips -Pmath2 filename.dvi
%     to print dvi file
% lpr -Pmath2 filename.ps
%     to print ps file


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\usepackage{graphicx,makeidx,amsmath,amssymb}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{setspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% settings:
%\author{Erik Erhardt} % Define the authors

%***% change title %***%
\title{John Muschelli  \hfill 02/11/1986 \hfill Biostatistics/Doctoral} % Define the title
%\pagestyle{headings} % Define the page style for page numbers and headings
%\addtolength{\textheight}{1cm}
%\makeindex

% Header
\usepackage{fancyhdr}
\pagestyle{fancy}

\newcommand{\company}{{Merck }}

\fancyhf{} % delete current setting for header and footer
\fancyhead[C]{\bf John Muschelli  \hfill muschellij2@gmail.com \hfill  \\
               Graduate-Level Internship \hfill Summer 2015 \hfill Cover Letter} %p.\thepage
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\headheight}{0.5pt} % make space for the rule
\fancypagestyle{plain}{%
       \fancyhead{} % get rid of headers on plain pages
       \renewcommand{\headrulewidth}{0pt} % and the line
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%==============
% \TempBox is needed for \undertilde and \undertildelow
\newbox\TempBox \newbox\TempBoxA
%
%======
% \undertilde will put an under_tilde that is close under the letter
%     use: \undertilde{d}
\def\undertilde#1{%
  \ifmmode\setbox\TempBox=\hbox{$#1$}\else\setbox\TempBox=\hbox{#1}\fi%
  \setbox\TempBoxA=\hbox to \wd\TempBox{\hss\char'176\hss}%
  \rlap{\copy\TempBox}\smash{\lower9pt\hbox{\copy\TempBoxA}}%
}
%
% \undertildelow will put an under_tilde that is low under the letter (easy to read)
%      use: \undertildelow{d}
\def\undertildelow#1{%
  \ifmmode\setbox\TempBox=\hbox{$#1$}\else\setbox\TempBox=\hbox{#1}\fi%
  \setbox\TempBoxA=\hbox to \wd\TempBox{\hss\char'176\hss}%
  \rlap{\copy\TempBox}\smash{\lower10pt\hbox{\copy\TempBoxA}}%
}
%%\newcommand{\cpp}{\ensuremath{\hbox{C}{++}}\xspace}
%%\DeclareRobustCommand{\Cpp}
%%\def\Cpp
%%{\valign{\vfil\hbox{##}\vfil\cr
%%   \textsf{C\kern-.1em}\cr
%%   $\hbox{\fontsize{\ssf@size}{0}\textbf{+\kern-0.05em+}}$\cr}%
%%}
%==============
%\maketitle     % generate the title
%\tableofcontents  %insert the table of contents
%\newpage
%\listoffigures
%\listoftables

%\newpage

%***% start problems here %***%
%***********************************************************************%

%%% see this tag for where the application needs to be changed on a university basis
% *** Mention of University here ***
% *** Mention of Time here ***

\hfill {\bf \today\\}

\doublespacing
For the past 5 years, I have done analysis on the MISTIE (Minimally Invasive Surgery Plus rt-PA for Intracerebral Hemorrhage Evacuation) and CLEAR (Clot Lysis: Evaluating Accelerated Resolution of Intraventricular Hemorrhage) clinical trials on stroke.  During this time, I have decreased revision time of reports, specifically reports to the data safety monitoring board (DSMB), by using automated report generation.  I used R alongside markdown and \LaTeX to create a standardized reporting structure for trial results.   

After receiving my Master's degree in Biostatistics, becoming a consultant for the Johns Hopkins Biostatistics Consulting Center (JHBC) on various projects.  I am 3 years into my PhD program of Biostatistics, I believe I understand the requirements and day-to-day life of an academic statistician.  I do not, however, understand the requirements of a biostatistician in an industry setting.  An internship in an industry position at \company will provide me insights into the roles I would have in that setting.

During my PhD, I have transitioned from the clinical trial aspects of our trials and focused more on the neuroimaging components of our data.  Although neuroimaging is now my primary focus, I have performed data cleaning and large-scale data analysis and have extensive experience with programming and pipeline development.  These skills cross many disciplines and I have found that nearly all operations can be more efficient and reliable if automated methods replace any manual steps.

Overall, I think \company is a leader in a number of fields, particularly in health care.  Working on projects that can directly help health care researchers and patients is ideal for my career, and an internship at \company provides the foundation for long-term, large-scale impact.






\end{document}
