%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% UMass Graduate Application Personal Statement
% Authors
%  Erik Erhardt
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Build this latex document with the following commands:
% latex filename.tex
% latex filename.tex
%     creates dvi file from tex file
% dvips filename.dvi
%     creases ps file from dvi file

% TO VIEW
% xdvi filename.dvi
%     to view dvi file
% ghostview filename.ps
%     to view ps file

% TO PRINT
% dvips -Pmath2 filename.dvi
%     to print dvi file
% lpr -Pmath2 filename.ps
%     to print ps file


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\usepackage{graphicx,makeidx,amsmath,amssymb}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% settings:
%\author{Erik Erhardt} % Define the authors

%***% change title %***%
\title{John Muschelli  \hfill 02/11/1986 \hfill Biostatistics/Doctoral} % Define the title
%\pagestyle{headings} % Define the page style for page numbers and headings
%\addtolength{\textheight}{1cm}
%\makeindex

% Header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % delete current setting for header and footer
\fancyhead[C]{\bf John Muschelli  \hfill DOB: 02/11/1986 \hfill Biostatistics/Doctoral \\
               Application for Admission \hfill Entrance Fall 2011 \hfill Personal Statement} %p.\thepage
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\headheight}{0.5pt} % make space for the rule
\fancypagestyle{plain}{%
       \fancyhead{} % get rid of headers on plain pages
       \renewcommand{\headrulewidth}{0pt} % and the line
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%==============
% \TempBox is needed for \undertilde and \undertildelow
\newbox\TempBox \newbox\TempBoxA
%
%======
% \undertilde will put an under_tilde that is close under the letter
%     use: \undertilde{d}
\def\undertilde#1{%
  \ifmmode\setbox\TempBox=\hbox{$#1$}\else\setbox\TempBox=\hbox{#1}\fi%
  \setbox\TempBoxA=\hbox to \wd\TempBox{\hss\char'176\hss}%
  \rlap{\copy\TempBox}\smash{\lower9pt\hbox{\copy\TempBoxA}}%
}
%
% \undertildelow will put an under_tilde that is low under the letter (easy to read)
%      use: \undertildelow{d}
\def\undertildelow#1{%
  \ifmmode\setbox\TempBox=\hbox{$#1$}\else\setbox\TempBox=\hbox{#1}\fi%
  \setbox\TempBoxA=\hbox to \wd\TempBox{\hss\char'176\hss}%
  \rlap{\copy\TempBox}\smash{\lower10pt\hbox{\copy\TempBoxA}}%
}
%%\newcommand{\cpp}{\ensuremath{\hbox{C}{++}}\xspace}
%%\DeclareRobustCommand{\Cpp}
%%\def\Cpp
%%{\valign{\vfil\hbox{##}\vfil\cr
%%   \textsf{C\kern-.1em}\cr
%%   $\hbox{\fontsize{\ssf@size}{0}\textbf{+\kern-0.05em+}}$\cr}%
%%}
%==============
%\maketitle     % generate the title
%\tableofcontents  %insert the table of contents
%\newpage
%\listoffigures
%\listoftables

%\newpage

%***% start problems here %***%
%***********************************************************************%

%%% see this tag for where the application needs to be changed on a university basis
% *** Mention of University here ***
% *** Mention of Time here ***

\hfill {\bf \today\\}

Before entering college, I deeply enjoyed biology, but had reservations about not pursuing a degree in a mathematics-related field.   The day I visited the University of Scranton, a professor described the biomathematics major and since then, the integration of both math and biology has fascinated me.  Biostatistics is one of the few fields that can help researchers describe natural phenomena and infer relationships about the world using rigorous tools. The fact that the fruits of this discipline can directly affect the treatment of diseases and clinical practice is a large reason why I would like to continue my education in biostatistics. \\
 
After working for over a year on Master's-level projects, I feel that I have become a leader and a resource for my colleagues. Furthermore, I have developed a desire for a deeper understanding of the field of biostatistics.   Also, I feel that learning cutting-edge statistical methods will increase my ability to tackle complex research problems.  Thus, I believe that obtaining a PhD in Biostatistics will help me to achieve these goals. \\

Working for the Johns Hopkins Biostatistics Consulting Center (JHBC) for the past year has provided me the opportunity to collaborate with experts in the field, work on a diversity of assignments, and acquire a competitive skill set. The various projects I have worked on include a multi-center stroke trial, an observational study of a pediatric intensive care unit, and functional MRI analysis in children with ADHD and autism. Through these projects, I have gained insight into the work of multidisciplinary biostatisticians. One commonality I have seen throughout is that one needs adequate \textbf{fundamentals} in order to produce the highest quality of work. \\

Although I have gained fundamental knowledge of biostatistics through my Master's program and work experience at JHBC, I would like to further broaden my knowledge and expertise. Therefore, to increase my knowledge and continue working on topics central to public health, applying to the program at the Harvard School of Public Health is a standout choice. Not only is this school one of the most respected public health institutions, but  it also has tremendous research opportunities.  As such, I would like to continue clinical trial research with the experts in this department.  \\
%I've greatly enjoyed my opportunity to work with MRI studies with my collaborators at the Kennedy Krieger Institute.  \\
%The professors are incomparable and the research ranges all aspects of public health.  \\

More importantly, the school fosters collaboration between researchers, clinicians, and most importantly, statisticians.  Overall, after spending three years within this field, I am confident that obtaining a PhD in Biostatistics is the necessary next step. This degree will inevitably provide me the tools and skills to approach complex and diverse problems. Ultimately, it will not only allow me to approach public health issues that not only interest me, but also think more analytically towards any problem.



\end{document}
