%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{John}
\familyname{Doe}
\title{Resumé title (optional)}               % optional, remove the line if not wanted
\address{street and number}{postcode city}    % optional, remove the line if not wanted
\mobile{mobile (optional)}                    % optional, remove the line if not wanted
\phone{phone (optional)}                      % optional, remove the line if not wanted
\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{email (optional)}                      % optional, remove the line if not wanted
\homepage{homepage (optional)}                % optional, remove the line if not wanted
\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{Part 1}



\section{ Personal Data}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.8in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
			Johns Hopkins School of Public Health, Department of Biostatistics: & \textit{Room:} E3148  \\
                          600 N Wolfe Street           & \textit{Cell:} (610) 291-7685 \\

  Baltimore, ~MD~21231~USA         & \textit{E-mail:}
\href{mailto:jmuschel@jhsph.edu}{jmuschel@jhsph.edu}\\
\textit{WWW:}
\href{http://www.jhsph.edu/faculty/directory/profile/5110/Muschelli/John}{http://www.jhsph.edu/faculty/directory/profile/5110/Muschelli/John} & \\
\end{tabular}

All links to sites are in blue and are clickable.  

\section{ \large Education and Training}
%
\href{http://www.biostat.jhsph.edu/}{\textbf{  Johns Hopkins School of Public Health}},
Baltimore, Maryland USA
\begin{outerlist}
\item[] ScM,
        \href{http://biostat.jhsph.edu/}
             {Biostatistics} (May 2010)
        \begin{innerlist}
        \item Thesis Topic: \emph{A Critical Review of HRF Derivatives in SPM for Functional Neuroimaging}
        \item Adviser:
              \href{http://www.biostat.jhsph.edu/~bcaffo/}
                   {Professor Brian Caffo}
        \item Area of Study: fMRI brain image data analysis\\
        \end{innerlist}
\end{outerlist}
        
\href{http://www.scranton.edu/}{\textbf{The University of Scranton}},
Scranton, Pennsylvania USA
\begin{outerlist}

\item[] B.S.,
        \href{http://math.scranton.edu/}
             {Biomathematics and Neuroscience}
            (Summa Cum Laude) (May 2008)
        \begin{innerlist}
        \item Adviser:
              \href{http://academic.scranton.edu/department/math/Faculty/inf_jasi.html}
                   {Professor Jakub Jasinski}
        \item Area of Study: Biomathematics\\
        \item Adviser:
              \href{http://academic.scranton.edu/faculty/cannon/}
                   {Professor J.~Timothy Cannon}
        \item Area of Study: Neuroscience
        \end{innerlist}


\end{outerlist}

\section{ Professional Experience}
%
\href{http://www.biostat.jhsph.edu/consult/}{\textbf{Johns Hopkins Biostatistics Center (JHBC)}},
Baltimore, Maryland USA
\begin{outerlist}

\item[] \textit{Junior Statistical Consultant}%
        \hfill \textbf{January 2009 to Present}
\begin{innerlist}
\item Collaborated on statistical projects with senior consultants.
\item Report writing and analyzing data using statistical software: R, Stata.
\item Cleaning and checking quality of data.
\end{innerlist}
\end{outerlist}



\href{http://lnir.kennedykrieger.org/staff.html}{\textbf{Laboratory for Neurocognitive and Imaging Research at Kennedy Krieger Institute}},
Baltimore, Maryland USA
\begin{outerlist}

\item[] \textit{Data Analyst}%
        \hfill \textbf{September 2010 to Present}
\begin{innerlist}
\item Analyzing functional MRI (fMRI) time series of participants.
\item Programming consultant: Matlab \& R.  
\end{innerlist}
\end{outerlist}



\href{http://www.analysisandinference.com/}{\textbf{Analysis \& Inference}},
Springfield, Pennsylvania USA
\begin{outerlist}

\item[] \textit{Statistical Assistant}%
        \hfill \textbf{June 2008 to August 2008}
\begin{innerlist}
\item Cooperated on statistical projects and conferenced with clients about possible analysis options.
\item Report writing of analyses: Stata
\item Data cleaning
\end{innerlist}

\end{outerlist}



\textbf{\href{http://www.dupont.com}{Dupont}},
Stine-Haskell Laboratory, Wilmington, Delaware USA
\begin{outerlist}
\item[] \textit{Research Interm}%
        \hfill \textbf{June 2007 to August 2007}
\begin{innerlist}
\item Developed lab skills and techniques: cell culturing, making and sterilizing broth media, optical density readings, inoculations, quality control, cell counts, screening for fungicidal properties of compounds.
\end{innerlist}

\end{outerlist}


\section{ Publications}
(In Review)  Newell, D. Shah, M. Wilcox, R. Hansmann, D, Melnychuk, E. Muschelli, J. Hanley, D. \textbf{Minimally invasive evacuation of spontaneous intracerebral hemorrhage using sonothrombolysis.} \emph{Journal of Neurosurgery}



(In Review) Jaffe, J.  Melnychuk, E. Muschelli, J. Ziai, W. Morgan, T.  Hanley, D.  Awad, Issam. \textbf{Ventricular catheter location and the clearance of intraventricular hemorrhage.}  \emph{Journal of Neurosurgery}


\section{ Honors and Awards}
%
\href{http://www.scranton.edu}{The University of Scranton}
\begin{innerlist}
\item Presidential Scholar (Full Tuition Scholarship), 2004-2008
\item Dean's List, 2004-2008
\item Alpha Lambda Delta, 2004
\item Alpha Sigma Nu, 2008

\end{innerlist}


\newpage
\section{Part 2}



\section{ \large Teaching Experience}
\href{http://www.jhsph.edu}{\textbf{Johns Hopkins School of Public Health}},
Baltimore, Maryland USA
\begin{outerlist}

\item[] \textit{Teaching Assistant}%
    \hfill \textbf{September 2010 to Present}
    \begin{innerlist}
        \item Biostatistics 621-4: Statistical Methods in Public Health I-IV
        \begin{innerlist}
            \item Responsible for 1~hour lab Stata session, 1~hour office hour, and grading homework, quizzes, and tests.
            \end{innerlist}~
  \hfill \textbf{September 2009 to May 2010}
        \item Biostatistics 651-4: Methods in Biostatistics I-IV
        \begin{innerlist}
            \item Responsible for 1~hour lab helping session, and grading homework and tests.
            \end{innerlist}~
  \hfill \textbf{January 2010}
        \item Biostatistics 613-4: Data Analysis Workshop I-II
        \begin{innerlist}
             \item Responsible for 4~hour lab and teaching session, helping students to get comfortable with Stata programming and interpreting results from output.

        \end{innerlist}~
    \end{innerlist}

\item[] \textit{Graduate Tutor}%
        \hfill \textbf{September 2009 to Present}
\begin{innerlist}
\item Tutored students in statistics on coursework and statistical dissertation material.
\end{innerlist}
\item[] \textit{Undergraduate Tutor}%
        \hfill \textbf{March 2005 to May 2008}
\begin{innerlist}
\item Tutored students regarding mathematics, statistics and other science courses.
\end{innerlist}
        
\end{outerlist}

\section{ Academic Service}
\href{http://incentivementoringprogram.org/}{Incentive Mentoring Program} 
\begin{outerlist}
\item[] \textit{Mentor}%
        \hfill \textbf{September 2010 to Present}
\begin{innerlist}
\item Mentor and tutor a student from Dunbar High School, teaching coursework, life skills, support as needed.
\end{innerlist}
\end{outerlist}



\href{www.scranton.edu}{University of Scranton}
\begin{outerlist}
\item[] \textit{Master of Ceremonies}
  \hfill \textbf{2005--2008}
\item Midnight Madness is a kickoff campaign for the basketball season and a food-raising activity for local food kitchens.  \item \href{http://www.theofficeconvention.com/}{The Office Convention} was an event where members of the television show The Office came to Scranton, students  entertained crowds in between events on the stages.  
\item Quizzo and Royal Feud are trivia games that are fundraisers for international and domestic service programs. 
\end{outerlist}



\href{http://academic.scranton.edu/organization/edjustice/events.shtml}{F.I.R.S.T. (Freshmen In Reflective Service Together)}
\begin{outerlist}
\item[] \textit{Leader} 
 \hfill \textbf{2007}
\item Led a service trip as a senior that welcomes incoming freshmen to participate in volunteer service at the University of Scranton.
\item Each team does service at various sites around the city of Scranton, namely Head Start, Little People Day Care, Lackawanna County Health Care Center.
\end{outerlist}



Saint Francis of Assisi Soup Kitchen, Scranton, PA
\begin{outerlist}
\item[] \textit{Volunteer}
\hfill \textbf{2004--2005}
\item Volunteered working with those running the soup kitchen.
\item Tasks ranged from cleaning dishes to handing out food.
\end{outerlist}


\section{ \large Technical Skills}
%
Software experience in statistics and data processing, cleaning, and basic data base management.  



\href{http://cran.r-project.org/}{\textsc{R}}
        experience: statistical programming, survival analysis, regression modeling, fmri image analysis, packages.



\href{http://www.sas.com}{\textsc{SAS}}
        experience: basic programming/analysis.



\href{http://www.stattransfer.com/}{\textsc{StatTransfer}}
        experience: import/export of multiple data formats.



\href{http://www.cs.uiowa.edu/~rlenth/StatWeave/}{\textsc{Statweave}}
        experience: programming multiple languages in one software.



\href{http://www.stata.com}{\textsc{Stata}}
        experience: statistical programming survival analysis, regression modeling.



\href{http://www.matlab.com}{\textsc{Matlab}}
        experience: intermediate programming, Statistical Parametric Mapping (SPM).  
        


Basic Programming: \href{http://www.cplusplus.com/}{C++}, \href{http://msdn.microsoft.com/en-us/vbasic/default}{Visual Basic}



Operating Systems: 
\setlength{\parindent}{0.5in}

\indent Proficient: Microsoft Windows XP/2000/Vista, Mac OS X.

\indent Novice: Linux CentOS5
\setlength{\parindent}{0in}



Applications: \TeX{}, \href{http://www.latex-project.org/}{\LaTeX{}}, B\textsc{ib}\TeX{}, Microsoft Office, OpenOffice, TeXShop, WinEdt, WinBUGS, MikTeX, Shell.  

\section{ Mathematical Experience}
%
Linear Algebra, Real Analysis



Probability, Random Variables, and Stochastic Processes, Statistical Inference, Survival Analysis



Statistical Programming



Functional MRI (fMRI) Analysis 
\nocite{*}
\bibliography{CV_20110711}
%\bibliography{CV_20110711}
\bibliographystyle{plain}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
